Depression and suicidality as costly signals of need

### 2021-02-19 Paper.rmd
Updated YAML header and r code in setup chunk.

---
title: "Depression and suicidality as costly signals of need"
author: "Michael Gaffney, Kai Adams, Kristen Syme, and Edward Hagen"
date: "2/18/2021"
output: html_document
---

@@

Compared to our pre-signal measures, we had more missing values in the post-signal questions. We attributed this to the fact that Qualtrics only records responses if the slider is touched, which most participants probably did not realize. Since the slider was preset at the center at Time 2, we assumed that the missing values were largely due to participants meaning to report no change. We therefore replaced the missing values with the middle value for Time 2 variables only. The minimum perent of a entries replaced was $`r signif(df_na_sum["Min."], 2)`$%, and the maximum was $`r signif(df_na_sum["Max."], 2)`$%, with the mean percentage of missing values replaced being $`r signif(df_na_sum["Mean"], 2)`$%. We did not replace missing values for Time 1 because the slider was preset to the far left (e.g. 0 percieved need).

>>>>

---
title: "Depression and suicidality as costly signals of need"
author: "Michael Gaffney, Kai Adams, Kristen L. Syme, and Edward H. Hagen"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
always_allow_html: true
output: 
  bookdown::html_document2:
    number_sections: false
bibliography: MTBib.bib
csl: apa-6th-edition.csl
---

```{r setup, include=F}
knitr::opts_chunk$set(echo = F, warning = F, error = F, message = F)
source('analysis.R')
```

@@

[deleted MA results stuff]
